VISUAL FEATURES OF INSCRIPTIONS. An issue for EDB (and EAGLE)

### 2016-05-04 source/40/Felle, Visual Features of inscriptions (EAGLE2016_Full_Paper).tex
FINAL folder added to hold all the edited files and final versions by La Sapienza; paper 40 by Felle added

% dummy text (remove in a normal thesis)
% remove if not necessary
\usepackage{siunitx}
%Natbib for bibliography management
\usepackage[authoryear]{natbib}
% custom commands
\newcommand{\bs}{\textbackslash}

@@

\newpage
On the open \emph{codex} is inscribed a focused - but barely readable - quotation from John 10, verses 7 and 9, where Jesus
indicates himself as the gate:

\begin{quotation}
John 10.7: \begin{otherlanguage*}{greek}
\underline{Εἶπεν} οὖν πάλιν ὁ ᾿Ιησοῦς, ᾿Αμὴν ἀμὴν λέγω ὑμῖν ὅτι \underline{ἐγώ εἰμι ἡ θύρα τῶν προβάτων}.
\end{otherlanguage*} (\emph{Therefore Jesus said again, ‘Very truly I tell you, I am the gate for the sheep});

John 10, 9: \begin{otherlanguage*}{greek}
ἐγώ εἰμι ἡ θύρα· \underline{δι' ἐμοῦ ἐάν τις εἰσέλθῃ} σωθήσεται καὶ \underline{εἰσελεύσεται καὶ ἐξελεύσεται καὶ νομὴν εὑρήσει}
\end{otherlanguage*}  ( $^\textit{9}$ \emph{I am the gate;
whoever enters through me will be saved.} $^{[a]}$ \emph{They will come in and go out, and find pasture}).

@@

\begin{quotation}
((crux)) \begin{otherlanguage*}{greek}
εἶπεν ὁ κ(ύριο)ς \textlatin{|} ἐγώ εἰμι \textlatin{|} ἡ θύρα τῶν \textlatin{|} προβάτων· \textlatin{|} δι᾿ ἐμοῦ \textlatin{||} ἐάν τις \textlatin{|} εἰσέλθῃ \textlatin{|} εἰσελεύσετ(αι) \textlatin{|} κ(αὶ) ἐξελεύσετ(αι) \textlatin{|} κ(αὶ) νομὴν \textlatin{|} εὑρήσει.
\end{otherlanguage*}

@@

\bibliographystyle{sapauth-eng}
\bibliography{../../EAGLE}

>>>>

% dummy text (remove in a normal thesis)
% remove if not necessary
\usepackage{siunitx}
%Natbib for bibliography management
\usepackage[authoryear]{natbib}
\bibpunct{(}{)}{;}{a}{}{,}
% custom commands
\newcommand{\bs}{\textbackslash}

@@

%\newpage
On the open \emph{codex} is inscribed a focused - but barely readable - quotation from John 10, verses 7 and 9, where Jesus
indicates himself as the gate:

\begin{quotation}
John 10.7: \selectlanguage{greek}
\underline{Εἶπεν} οὖν πάλιν ὁ ᾿Ιησοῦς, ᾿Αμὴν ἀμὴν λέγω ὑμῖν ὅτι \underline{ἐγώ εἰμι ἡ θύρα τῶν προβάτων}.
\selectlanguage{english} (\emph{Therefore Jesus said again, ‘Very truly I tell you, I am the gate for the sheep});

John 10, 9: \selectlanguage{greek}
ἐγώ εἰμι ἡ θύρα· \underline{δι' ἐμοῦ ἐάν τις εἰσέλθῃ} σωθήσεται καὶ \underline{εἰσελεύσεται καὶ ἐξελεύσεται καὶ νομὴν εὑρήσει}
\selectlanguage{english}  ( $^\textit{9}$ \emph{I am the gate;
whoever enters through me will be saved.} $^{[a]}$ \emph{They will come in and go out, and find pasture}).

@@

\begin{quotation}
((crux)) \selectlanguage{greek}
εἶπεν ὁ κ(ύριο)ς \textlatin{|} ἐγώ εἰμι \textlatin{|} ἡ θύρα τῶν \textlatin{|} προβάτων· \textlatin{|} δι᾿ ἐμοῦ \textlatin{||} ἐάν τις \textlatin{|} εἰσέλθῃ \textlatin{|} εἰσελεύσετ(αι) \textlatin{|} κ(αὶ) ἐξελεύσετ(αι) \textlatin{|} κ(αὶ) νομὴν \textlatin{|} εὑρήσει.
\selectlanguage{english}

@@

\bibliographystyle{sapienza-chicago}
\bibliography{../../EAGLE}
